# MIDS

MIDS provides tools for applying **Multi-frame Individual Distinction by Size** to stereo-video observations.

The package estimates the number of distinct individuals observed within a camera deployment by comparing length measurements across frames while accounting for measurement precision.

## Installation

During development, load the package from the project folder using:

```{r, eval=FALSE}
pkgload::load_all()
```

After installation, MIDS can be loaded with:

```{r, eval=FALSE}
library(MIDS)
```

## Example

```{r example}
test_data <- data.frame(
  CameraID = c("C1","C1","C1","C1","C2","C2"),
  Frame = c(1,1,2,2,1,2),
  Species = c("A","A","A","A","A","A"),
  Length = c(105,112,109,150,98,104),
  Precision_Error = c(2.5,2.0,3.0,2.5,1.8,2.2)
)

results <- run_mids(
  data = test_data,
  group_cols = c("CameraID", "Species"),
  frame_col = "Frame",
  length_col = "Length",
  precision_col = "Precision_Error"
)

results
```

## Summary

```{r}
summarise_mids(test_data, results)
```

## Summary by group

```{r}
summarise_mids_by_group(
  original_data = test_data,
  mids_results = results,
  group_cols = c("CameraID", "Species")
)
```

## Required columns

MIDS requires:

- a grouping structure, usually camera/deployment and species
- a frame or time column
- a fish length column
- a measurement precision/error column

For example:

```{r, eval=FALSE}
run_mids(
  data = fish_data,
  group_cols = c("DeploymentID", "Species"),
  frame_col = "Frame",
  length_col = "Length_mm",
  precision_col = "Precision_Error"
)
```

## Notes

`group_cols` should define the level within which fish may represent repeat observations of the same individual. At minimum, this should usually include a camera, deployment, or video identifier and species.
